An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-05-08 simplified_sdc_intro/paper.tex
update table with latest runs

\begin{deluxetable}{llll}
\tablecaption{\label{table:masses} Species masses.}
\tablehead{\colhead{simulation} & \colhead{$M_{\isotm{He}{4}}$} & \colhead{$M_{\isotm{Si}{28}}$} & \colhead{$M_{\isotm{Ni}{56}}$}}
\startdata
\multicolumn{4}{c}{Strang runs} \\
\hline
{\tt strang\_subch2\_cfl0.2}           & $6.10\times 10^{31}$ & $6.72\times 10^{31}$ & $5.29\times 10^{31}$ \\
{\tt strang\_subch2\_cfl0.4}           & $5.20\times 10^{31}$ & $6.70\times 10^{31}$ & $6.02\times 10^{31}$ \\
{\tt strang\_subch2\_cfl0.4\_mixedtol} & $3.05\times 10^{31}$ & $7.29\times 10^{31}$ & $7.80\times 10^{31}$ \\
{\tt strang\_subch2\_cfl0.8}           & $4.59\times 10^{31}$ & $6.88\times 10^{31}$ & $6.27\times 10^{31}$ \\
\hline
\multicolumn{4}{c}{SDC runs} \\
\hline
{\tt sdc\_subch2\_cfl0.2}           & $3.35\times 10^{31}$  & $7.26\times 10^{31}$  & $8.27\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.4}           & $3.30\times 10^{31}$  & $7.27\times 10^{31}$  & $8.13\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.4\_mixedtol} & $3.09\times 10^{31}$  & $7.36\times 10^{31}$  & $8.08\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.4\_tol1.e-6} & $3.25\times 10^{31}$  & $7.27\times 10^{31}$  & $8.25\times 10^{31}$ \\
{\tt sdc\_subch2\_cfl0.8}           & $3.18\times 10^{31}$  & $7.34\times 10^{31}$  & $7.83\times 10^{31}$ \\
\enddata
\end{deluxetable}

>>>>

\begin{deluxetable}{llll}
\tablecaption{\label{table:masses} Species masses.}
\tablehead{\colhead{simulation} & \colhead{$M_{\isotm{He}{4}}$} & \colhead{$M_{\isotm{Si}{28}}$} & \colhead{$M_{\isotm{Ni}{56}}$}}
\startdata
\multicolumn{4}{c}{Strang runs} \\
\hline
{\tt strang\_subch2\_cfl0.1}           & 1.059\times 10^{32}  &  3.804\times 10^{31}  &  1.092\times 10^{32} \\
{\tt strang\_subch2\_cfl0.2}           & 9.114\times 10^{31}  &  4.174\times 10^{31}  &  1.078\times 10^{32} \\
{\tt strang\_subch2\_cfl0.2\_tol1.e-8} & 7.222\times 10^{31}  &  8.623\times 10^{31}  &  4.041\times 10^{31} \\
{\tt strang\_subch2\_cfl0.4}           & 7.819\times 10^{31}  &  4.208\times 10^{31}  &  1.045\times 10^{32} \\
\hline
\multicolumn{4}{c}{SDC runs} \\
\hline
{\tt sdc\_subch2\_cfl0.1}           & 7.319\times 10^{31}  &  9.147\times 10^{31}  &  3.765\times 10^{31} \\
{\tt sdc\_subch2\_cfl0.2}           & 7.208\times 10^{31}  &  9.151\times 10^{31}  &  3.783\times 10^{31} \\
{\tt sdc\_subch2\_cfl0.2\_tol1.e-8} & 7.376\times 10^{31}  &  9.220\times 10^{31}  &  3.513\times 10^{31} \\
{\tt sdc\_subch2\_cfl0.4}           & 7.203\times 10^{31}  &  8.843\times 10^{31}  &  3.754\times 10^{31} \\
\hline
\enddata
\end{deluxetable}
